Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-24 manuscript/manuscript.Rmd
Adding to methods section.

A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.

>>>>

Causality can be inferred through conjoint analysis because it shows which components of a choice hold the most weight. Conjoint analysis has been widely used within social sciences and has recently begun to be used in political and public policy fields. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess tradeoffs made in political communications. ### rewrite in more detail so that it's clear that consumers are making the tradeoffs ### Conjoint is key in political research because it captures multidimensional causal relations.

Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgement of credibility. Public policy research would benefit from conjoint analysis for the same reasons.
